HEP Software Foundation Community White Paper Working Group -- Training, Staffing and Careers

### 2018-06-14 CWP/papers/HSF-CWP-2017-02_training/latex/cwp-wg-training-careers.tex
Two subsections for training needs.

The HEP user community consists of a set of users with diverse software
experience, interests, and time availablity to learn new techniques.  Any
training program must take into account the variation in target audiences. For
example, an undergraduate doing a summer research project has different needs
and skills than their mentoring professor.
For purposes of training, it is useful to think of all our user community as
\emph{students}. More specifically, we can broadly identify four different sets
of students, classified by experience level, recognizing that even within these
groups there will be people who will learn at different speeds and with
differing depths of understanding:

>>>>

The HEP user community consists of a set of users with diverse software
experience, interests, and time availablity to learn new techniques.  Any
training program must take into account the variation in target audiences. For
example, an undergraduate doing a summer research project has different needs
and skills than their mentoring professor. For purposes of training, we will
name all our user community as \emph{students}.

%____________________________________________________________________
\subsection{Classification of trainees}

We can broadly identify four different sets of students, classified by experience level,
recognizing that even within these groups there will be people who will learn at different
speeds and with differing depths of understanding:
